---
title: "Homework 1"
author: "Yuixn"
---

```{r setup,include=FALSE}
library(tidyverse)
```
## Problem 1
##create data frame
```{r }
problem1_df = tibble(
  vec_runiform = runif(10,min=0,max=5),
  vec_logical = output_column(vec_runiform > 2),
  vec_character = c("My","name","is","Yuxin","I","love","Data","Science","a","lot"),
  vec_factor = factor(c("male", "male", "female", "female","male","female","male","female","male","male"))
)
problem1_df
```
* The mean of the numerical vector is `r mean(problem1_df$vec_runiform)`
* The mean of the logical vector is `r mean(problem1_df$vec_logical)`
* The mean of the character vector is `r mean(problem1_df$vec_character)`
* The mean of the factor vector is `r mean (problem1_df$vec_factor)`


I can find the mean of the numerical and logical vector, and the result of the mean of character and factor vector is not working. This happened due to that mean function in R find the arithmetic mean of the variable. Only variable with a number will make sense under mean function.